---
title: "Homework 1"
author: "Ahmet Hamdi Çakmak-20080382" 
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.

I love my **friends.**

**Question 2** With Markdown write a sentence that has one word in italic.

I like *computer* games.

**Question 3** With Markdown write a sentence that has one word in italic bold.

He bought a new ***Ferrari***.

**Question 4** With Markdown write an unordered list with three items.

\*Orange

\*Banana

\*Cherry

\*Apricot

**Question 5** With Markdown write an ordered list with three items.

1.  Napoli

2.  Arsenal

3.  Braga

4.  Sevilla

**Question 6** With Markdown give a link to your favorite webpage.

[Youtube!](https://www.youtube.com/)

**Question 7** With Markdown add a cat picture.

[cat!](https://www.daysoftheyear.com/cdn-cgi/image/dpr=1%2Cf=auto%2Cfit=cover%2Cheight=675%2Cq=85%2Cwidth=1200/wp-content/uploads/international-cat-day1-scaled.jpg)

**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

```{r}
head(pressure)
summary(pressure)

```

**Question 9** With $LaTeX$ write your favorite equation in block form.

$$
\sqrt{\frac{a}{b}}
$$

**Question 10** In a code chunk calculate 3 + 4.

    ## [1] 7
